\textbf{Using the MSU Thesis Class}

### 2024-05-01 docs/msu-thesis.tex
Added note to the docs about missing leaders in the TOC

>>>>

If your chapter titles are very long, they sometimes fail to put any leader dots before the page number in the Table of Contents. The thesis office requires a minimum of three dots of leaders for any TOC line. You can solve this problem by putting a line break  into the TOC entry title. To do this, use the optional argument of the corresponding |\chapter| or |\section| etc. command. Note that the line break needs to be preceded by |\protect|.

%\begin{quote}
\begin{lstlisting}[frame=none,xleftmargin=2.5em]
\chapter[Long chapter title that will\protect\\ break at this point]
        {Long chapter title that will break at this point}
\end{lstlisting}
%\end{quote}
